{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2020-11-25 documents/viscosity.tex
Huh, viscous damping works out

@@

To compare with Yang's results, Influenza A. Density is equal to that of the surrounding solution: $\rho_{liquid} = \rho_{solid} = 1000 \text{kg/m}^3$. R = 50 nm. An approximate c=1000 m/s is used. Viscosity of $\mu=10e-3 Ns/m^2$ is used.

$$ b = \frac{4\mu}{R^2 \rho_{solid}} = \frac{4 \cdot 1\times 10^{-3}\  \text{N}\cdot \text{s} / \text{m}^2 }{(50 \text{nm})^2 1000 \text{kg /m}^2} = 1.6 \times 10^9\ \text{N}\cdot \text{s} /( \text{m}\cdot\text{kg})$$

Where $\mu$ is the viscosity of the fluid, R is the radius of the sphere, $\rho_{solid}$. \footnotemark

@@

@@

$$\gamma = \frac{b}{2m} = $$

Finally,

$$ \omega_{res} = \sqrt{\frac{(\rho_{solid} / \rho_{liquid})c^2}{R^2}} $$

>>>>

Let us use a first-order Fermi estimate of the drag force to see if speculative mechanisms are required.

@@

To compare with Yang's results, Influenza A. Density is equal to that of the surrounding solution: $\rho_{liquid} = \rho_{solid} = 1000 \text{kg/m}^3$. R = 50 nm. Viscosity of $\mu=10e-3 Ns/m^2$ is used.

$$ \gamma = \frac{4\mu}{R^2 \rho_{solid}} = \frac{4 \cdot 1\times 10^{-3}\  \text{N}\cdot \text{s} / \text{m}^2 }{(50 \text{nm})^2 1000 \text{kg /m}^2} = 1.6 \times 10^9 \text{s}^{-1} = 1.6\ \text{GHz}$$

Where $\mu$ is the viscosity of the fluid, R is the radius of the sphere, $\rho_{solid}$. \footnotemark \footnotemark

@@

\footnotetext{Persson seems to go against modern convention, using 1/s as the damping in the differential equation.}

@@

Finally, where the densities of the two materials are equal (a reasonable approximation), An approximate c=1000 m/s is used.

$$ \omega_{res} = c / R = 20 \text{GHz}$$

This is about double that seen by Sun. Most critically, however,

$$ Q = \omega_{res}/(2\gamma) = 6.25 $$

Which is distinctly in the underdamped regime.

Contrast this with Adair's arguments along the same lines reporting sub-picosecond relaxation times.

However, if we apply the same arguments to microtubules \cite{Viscous2000}, omega_c = 80 GHz, and Q=11.2. Such an effect is so trivial that we find it hard to believe.
